---
title: "Final Project"
author: "Malcolm Smith Fraser"
date: "10/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(dplyr)
library(ggplot2)
library(pander)
library(tidyverse)
library(gridExtra)
library(caret)
library(e1071)
library(arm)
library(pROC)
```

There do appear to be some missing values (4 in 'ca', and 2 in 'thal')
Dropping all rows with na values drops 6 rows (303 -> 297)
```{r cars}
cleveland <- read.csv('cleaned_cleveland.csv',header = TRUE)
cleveland$sex <- factor(cleveland$sex, 
                       levels = c(0,1), 
                       labels = c('female','male')
                       )
cleveland$cp =  factor(cleveland$cp, 
                       levels = c(1,2,3,4), 
                       labels = c('typical angina',
                                  'atypical angina',
                                  'non-anginal pain',
                                  'asymptomatic')
                       )
cleveland$exang <- factor(cleveland$exang, 
                         levels = c(0,1), 
                         labels = c('no','yes')
                         )
cleveland$slope <- factor(cleveland$slope, 
                         levels = c(1,2,3), 
                         labels = c('unsloping','flat','downsloping')
                         )
cleveland$ca <- as.factor(cleveland$ca)
cleveland$thal <- factor(cleveland$thal, 
                        levels = c(3,6,7), 
                        labels = c("normal","fixed defect", "reversable defect")
                        )
cleveland$numm <- as.factor(cleveland$num)
cleveland$num <- factor(cleveland$num, 
                       levels = c(0,1), 
                       labels = c("NoDiagnosis","Diagnosis")
                       )
cleveland$fbs <- factor(cleveland$fbs, 
                       levels = c(0,1), 
                       labels = c("Under 120mg/dl","Over 120mg/dl")
                       )
cleveland$restecg <- factor(cleveland$restecg, 
                           levels = c(0,1,2), 
                           labels = c("Normal","ST-T wave abnormality","LV Hypertophy")
                           )
cleveland$trestbps <- cleveland$trestbps - mean(cleveland$trestbps)
cleveland$age <- cleveland$age - mean(cleveland$age)
cleveland$chol <- cleveland$chol - mean(cleveland$chol)
cleveland$thalach <- cleveland$thalach - mean(cleveland$thalach)
cleveland$oldpeak <- cleveland$oldpeak - mean(cleveland$oldpeak)

cleveland = drop_na(cleveland)

summary(cleveland)
str(cleveland)
nrow(cleveland)
```
```{r, echo=F}
plot(cleveland$num)
```

# Factor variables and interactions
Looks like if you have exercised induced angina the probability that you have heart disease is significantly higher
Also looks like the probability that you have heart disease is significantly higher if you are asymptimatic in terms of chest pain 
```{r, echo = F}
pander(tapply(cleveland$num, cleveland$cp, function(x) table(x)/sum(table(x))))
pander(tapply(cleveland$num, cleveland$exang, function(x) table(x)/sum(table(x))))

```

For every level of chest pain (including asymptomatic) except for typical angina, the probability of having heart disease is greater for patients who are experiencing exercise induced angina. This could be dut to the fact that if you are experiencing typical angina, the probability that you are also experiencing angina during exercise is likely higher regardless of if you have heart disease.

```{r, echo = F}
pander(tapply(cleveland$num[cleveland$exang == 'no'], cleveland$cp[cleveland$exang == 'no'], function(x) table(x)/sum(table(x))))
pander(tapply(cleveland$num[cleveland$exang == 'yes'], cleveland$cp[cleveland$exang == 'yes'], function(x) table(x)/sum(table(x))))

```

Asymptomatic women a are more likely to have a diagnosis 
```{r, echo = F}
pander(tapply(cleveland$num[cleveland$sex == 'male'], cleveland$cp[cleveland$sex == 'male'], function(x) table(x)/sum(table(x))))
pander(tapply(cleveland$num[cleveland$sex == 'female'], cleveland$cp[cleveland$sex == 'female'], function(x) table(x)/sum(table(x))))
```

```{r, echo = F}
tapply(cleveland$num[cleveland$fbs == 'Under 120mg/dl'], cleveland$cp[cleveland$fbs == 'Under 120mg/dl'], function(x) table(x)/sum(table(x)))
tapply(cleveland$num[cleveland$fbs == 'Over 120mg/dl'], cleveland$cp[cleveland$fbs == 'Over 120mg/dl'], function(x) table(x)/sum(table(x)))
```

```{r, echo = F}
pander(tapply(cleveland$num[cleveland$restecg  == 'Normal'], cleveland$cp[cleveland$restecg  == 'Normal'], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$restecg  == 'Normal'])
pander(tapply(cleveland$num[cleveland$restecg  == 'ST-T wave abnormality'], cleveland$cp[cleveland$restecg  == 'ST-T wave abnormality'], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$restecg  == 'ST-T wave abnormality'])
pander(tapply(cleveland$num[cleveland$restecg  == "LV Hypertophy"], cleveland$cp[cleveland$restecg  == "LV Hypertophy"], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$restecg  == "LV Hypertophy"])
```

Some values are 0 or 1 thus we cant includein the model (will throw error)
```{r, echo = F}
tapply(cleveland$num[cleveland$slope == 'unsloping'], cleveland$cp[cleveland$slope == 'unsloping'], function(x) table(x)/sum(table(x)))
table(cleveland$cp[cleveland$slope == 'unsloping'])
tapply(cleveland$num[cleveland$slope == 'flat'], cleveland$cp[cleveland$slope == 'flat'], function(x) table(x)/sum(table(x)))
table(cleveland$cp[cleveland$slope == 'flat'])
tapply(cleveland$num[cleveland$slope == 'downsloping'], cleveland$cp[cleveland$slope == 'downsloping'], function(x) table(x)/sum(table(x)))
table(cleveland$cp[cleveland$slope == 'downsloping'])
```

Potential interaction between cp and thal but insufficeint obersations at each level to consider interactions
```{r, echo = F}
pander(tapply(cleveland$num[cleveland$thal == 'normal'], cleveland$cp[cleveland$thal == 'normal'], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$thal == 'normal'])
pander(tapply(cleveland$num[cleveland$thal == 'fixed defect'], cleveland$cp[cleveland$thal == 'fixed defect'], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$thal == 'fixed defect'])
pander(tapply(cleveland$num[cleveland$thal == 'reversable defect'], cleveland$cp[cleveland$thal == 'reversable defect'], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$thal == 'reversable defect'])
```
may be interaction between cp and ca
```{r, echo = F}
pander(tapply(cleveland$num[cleveland$ca == 0], cleveland$cp[cleveland$ca == 0], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$ca == 0])
pander(tapply(cleveland$num[cleveland$ca == 1], cleveland$cp[cleveland$ca == 1], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$ca == 1])
pander(tapply(cleveland$num[cleveland$ca == 2], cleveland$cp[cleveland$ca == 2], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$ca == 2])
pander(tapply(cleveland$num[cleveland$ca == 3], cleveland$cp[cleveland$ca == 3], function(x) table(x)/sum(table(x))))
table(cleveland$cp[cleveland$ca == 3])
table(cleveland$ca)
```

# Continuous variables and interactions

The repationship between age and heart disease is generally unchaged given different types of angina, with diseased patients being older than non-patients. However, diseased patients experiencing typical angina do appear to be roughly the same age an non diseased patients with the same angina classification

Potantial interaction between thal and age
slight interaction betweem thal and trestbps
```{r age EDA, echo=FALSE}
##### AGE #####
p1 = ggplot(cleveland, aes(x=age, y=num, fill=num)) +
              geom_boxplot();p1

### Interactions with chest pain
p6 = ggplot(cleveland, aes(x=age, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~cp);p6
p7 = ggplot(cleveland, aes(x=age, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~exang);p7
p7a = ggplot(cleveland, aes(x=age, y=num, fill=exang)) +
              geom_boxplot() +
              facet_wrap(~cp);p7a

### Interactions with other factor variables

p8a = ggplot(cleveland, aes(x=age, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~sex);p8a
p8b = ggplot(cleveland, aes(x=age, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~fbs);p8b
p8c = ggplot(cleveland, aes(x=age, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~restecg);p8c
p8d = ggplot(cleveland, aes(x=age, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~slope);p8d
p8e = ggplot(cleveland, aes(x=age, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~thal);p8e ###
p8f = ggplot(cleveland, aes(x=age, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~ca);p8f

table(cleveland$age[cleveland$ca == 3])
```

No apparent interactions between trestbps and either type of chest pain
Potential interaction beteeen sex and trestbps (and maybe trestbps and fbs)
slight interaction between trestbps and ca
```{r trestbps EDA, echo=F}
##### TRESTBPS #####
p2 = ggplot(cleveland, aes(x=trestbps, y=num, fill=num)) +
              geom_boxplot();p2

### Interactions with chest pain
p8 = ggplot(cleveland, aes(x=trestbps, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~cp);p8
p9 = ggplot(cleveland, aes(x=trestbps, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~exang);p9
p9a = ggplot(cleveland, aes(x=trestbps, y=num, fill=exang)) +
              geom_boxplot() +
              facet_wrap(~cp);p9a

### Interactions with other factor variables
p10a = ggplot(cleveland, aes(x=trestbps, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~sex);p10a ###
p10b = ggplot(cleveland, aes(x=trestbps, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~fbs);p10b
p10c = ggplot(cleveland, aes(x=trestbps, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~restecg);p10c
p10d = ggplot(cleveland, aes(x=trestbps, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~slope);p10d
p10e = ggplot(cleveland, aes(x=trestbps, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~thal);p10e
p10f = ggplot(cleveland, aes(x=trestbps, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~ca);p10f
table(cleveland$num[cleveland$ca == 3])
```

(MAYBE) slight interaction between chol and cp
No other apparent interactions with chol
Slight interaction between chol and ca
```{r chol EDA, echo=F}
##### CHOL #####
p3 = ggplot(cleveland, aes(x=chol, y=num, fill=num)) +
              geom_boxplot();p3

### Interactions with chest pain
p10 = ggplot(cleveland, aes(x=chol, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~cp);p10
p11 = ggplot(cleveland, aes(x=chol, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~exang);p11
p11a = ggplot(cleveland, aes(x=chol, y=num, fill=exang)) +
              geom_boxplot() +
              facet_wrap(~cp);p11a

### Interactions with other factor variables
p12a = ggplot(cleveland, aes(x=chol, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~sex);p12a ###
p12b = ggplot(cleveland, aes(x=chol, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~fbs);p12b
p12c = ggplot(cleveland, aes(x=chol, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~restecg);p12c
p12d = ggplot(cleveland, aes(x=chol, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~slope);p12d
p12e = ggplot(cleveland, aes(x=chol, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~thal);p12e
p12f = ggplot(cleveland, aes(x=chol, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~ca);p12f
table(cleveland$cp)
```

No apparent interactions with thalach
```{r thalach EDA, echo=F}
##### THALACH #####
p4 = ggplot(cleveland, aes(x=thalach, y=num, fill=num)) +
              geom_boxplot();p4

### Interactions with chest pain
p12 = ggplot(cleveland, aes(x=thalach, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~cp);p12
p13 = ggplot(cleveland, aes(x=thalach, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~exang);p13
p13a = ggplot(cleveland, aes(x=thalach, y=num, fill=exang)) +
              geom_boxplot() +
              facet_wrap(~cp);p13a

### Interactions with other factor variables
p14a = ggplot(cleveland, aes(x=thalach, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~sex);p14a
p14b = ggplot(cleveland, aes(x=thalach, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~fbs);p14b
p14c = ggplot(cleveland, aes(x=thalach, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~restecg);p14c
p14d = ggplot(cleveland, aes(x=thalach, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~slope);p14d
p14e = ggplot(cleveland, aes(x=thalach, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~thal);p14e
p14f = ggplot(cleveland, aes(x=thalach, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~ca);p14f
```

(MAYBE) slight interaction between oldpeak and cp
```{r oldpeak EDA, echo=F}
##### OLDPEAK #####
p5 = ggplot(cleveland, aes(x=oldpeak, y=num, fill=num)) +
              geom_boxplot();p5

### Interactions with chest pain
p14 = ggplot(cleveland, aes(x=oldpeak, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~cp);p14
p15 = ggplot(cleveland, aes(x=oldpeak, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~exang);p15
p15a = ggplot(cleveland, aes(x=oldpeak, y=num, fill=exang)) +
              geom_boxplot() +
              facet_wrap(~cp);p15a

### Interactions with other factor variables
p15a = ggplot(cleveland, aes(x=oldpeak, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~sex);p15a ###
p15b = ggplot(cleveland, aes(x=oldpeak, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~fbs);p15b
p15c = ggplot(cleveland, aes(x=oldpeak, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~restecg);p15c
p15d = ggplot(cleveland, aes(x=oldpeak, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~slope);p15d
p15e = ggplot(cleveland, aes(x=oldpeak, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~thal);p15e
p15f = ggplot(cleveland, aes(x=oldpeak, y=num, fill=num)) +
              geom_boxplot() +
              facet_wrap(~ca);p15f
```


# Modelling

When looking at chest pain alone, does
```{r, echo=F}
#Selecting the null model

model_bare <- glm(num ~ 1, data = cleveland, family = binomial)
summary(model_bare)
rawresid_bare <- residuals(model_bare,"resp")
binnedplot(x=fitted(model_bare),y=rawresid1,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_bare <- confusionMatrix(as.factor(ifelse(fitted(model_bare) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_bare


model_cp <- glm(num ~ relevel(cp,ref='asymptomatic'), data = cleveland, family = 'binomial')
summary(model_cp)
rawresid_cp <- residuals(model_cp,"resp")
binnedplot(x=fitted(model_cp),y=rawresid_cp,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_cp <- confusionMatrix(as.factor(ifelse(fitted(model_cp) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_cp

model_exang <- glm(num ~ exang, data = cleveland, family = 'binomial')
summary(model_exang)
rawresid_exang <- residuals(model_exang,"resp")
binnedplot(x=fitted(model_exang),y=rawresid_cp,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_exang <- confusionMatrix(as.factor(ifelse(fitted(model_exang) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_exang

### Best Null model below
model_cpex <- glm(num ~ cp*exang, data = cleveland, family = 'binomial')
summary(model_cpex)
rawresid_cpex <- residuals(model_cpex,"resp")
binnedplot(x=fitted(model_cpex),y=rawresid_cpex,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_cpex <- confusionMatrix(as.factor(ifelse(fitted(model_cpex) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_cpex

mean(cleveland$num_num)
```

```{r, echo=F}
model_1 <- glm(num ~ cp + age, data = cleveland, family = 'binomial');summary(model_1)
anova(model_cp, model_1) #Deviance -9.62
rawresid_1 <- residuals(model_1,"resp")
confmat_1 <- confusionMatrix(as.factor(ifelse(fitted(model_1) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_1

model_2 <- glm(num ~ cp + sex, data = cleveland, family = 'binomial');summary(model_2)
anova(model_cp, model_2) #Deviance -22.44
rawresid_2 <- residuals(model_2,"resp")
confmat_2 <- confusionMatrix(as.factor(ifelse(fitted(model_2) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_2

model_3 <- glm(num ~ cp + trestbps, data = cleveland, family = 'binomial');summary(model_3)
anova(model_cp, model_3) #Deviance -6.99
rawresid_3 <- residuals(model_3,"resp")
confmat_3 <- confusionMatrix(as.factor(ifelse(fitted(model_3) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_3

model_4 <- glm(num ~ relevel(cp,ref = 'asymptomatic') * chol, data = cleveland, family = 'binomial');summary(model_4)
anova(model_cp, model_4) #Deviance -0.98
rawresid_4 <- residuals(model_4,"resp")
confmat_4 <- confusionMatrix(as.factor(ifelse(fitted(model_4) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_4

model_5 <- glm(num ~ cp + fbs, data = cleveland, family = 'binomial');summary(model_5)
anova(model_cp, model_5) #Deviance -0.773
rawresid_5 <- residuals(model_5,"resp")
confmat_5 <- confusionMatrix(as.factor(ifelse(fitted(model_5) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_5

model_6 <- glm(num ~ cp + restecg, data = cleveland, family = 'binomial');summary(model_6)
anova(model_cp, model_6) #Deviance -4.66
rawresid_6 <- residuals(model_6,"resp")
confmat_6 <- confusionMatrix(as.factor(ifelse(fitted(model_6) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_6

model_7 <- glm(num ~ relevel(cp,ref='asymptomatic') + thalach, data = cleveland, family = 'binomial');summary(model_7)
anova(model_cp, model_7) #Deviance -25.038
binnedplot(x=fitted(model_7),y=rawresid_cp,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
rawresid_7 <- residuals(model_7,"resp")
confmat_7 <- confusionMatrix(as.factor(ifelse(fitted(model_7) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_7

model_8 <- glm(num ~ relevel(cp,ref='asymptomatic') * oldpeak, data = cleveland, family = 'binomial');summary(model_8)
anova(model_cp, model_8) #Deviance -37.60
rawresid_8 <- residuals(model_8,"resp")
confmat_8 <- confusionMatrix(as.factor(ifelse(fitted(model_8) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_8

model_9 <- glm(num ~ cp + slope, data = cleveland, family = 'binomial');summary(model_9)
anova(model_cp, model_9) #Deviance -27.65
rawresid_9 <- residuals(model_1,"resp")
confmat_9 <- confusionMatrix(as.factor(ifelse(fitted(model_9) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_9

model_10 <- glm(num ~ relevel(cp,ref='asymptomatic') + relevel(ca,ref='3'), data = cleveland, family = 'binomial');summary(model_10)
anova(model_cp, model_10) #Deviance -47.33
rawresid_10 <- residuals(model_10,"resp")
confmat_10 <- confusionMatrix(as.factor(ifelse(fitted(model_10) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_10

model_11 <- glm(num ~ relevel(cp,ref='asymptomatic') + thal, data = cleveland, family = 'binomial');summary(model_11)
anova(model_cp, model_11) #Deviance -52.90
rawresid_11 <- residuals(model_11,"resp")
confmat_11 <- confusionMatrix(as.factor(ifelse(fitted(model_11) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_11
```
thal (model_11) (130/97)
ca (model_10) (114/111)
oldpeak (model_8) (118/110) 
slope (model_9) (121/103)
thalach (model_7) (125/105)
sex (model_2) (121/103)

age (model_1) (121/103)
trestbps (model_3) (121/103)
restecg (model_6) (121/103)

chol (model_4) (121/103)
fbs (model_5) (121/103)


```{r, echo=F}
model_thalach <- glm(num ~ thalach, data = cleveland, family = 'binomial');summary(model_thalach)
anova(model_thalach, model_7) #Deviance -25.038
rawresid_thalach <- residuals(model_thalach,"resp")
confmat_thalach <- confusionMatrix(as.factor(ifelse(fitted(model_thalach) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis"); confmat_thalach
```
```{r, echo=F}
model_cp_sex <- glm(num ~ relevel(cp,ref='asymptomatic')*relevel(sex,ref='male'), data = cleveland, family = 'binomial');summary(model_cp_sex)
rawresid_cp_sex <- residuals(model_cp_sex,"resp")
binnedplot(x=fitted(model_cp_sex),y=rawresid_cp_sex,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_cp_sex <- confusionMatrix(as.factor(ifelse(fitted(model_cp_sex) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_cp_sex

```

```{r, echo=F}
model_cp_sex <- glm(num ~ relevel(cp,ref='asymptomatic')*relevel(sex,ref='male') + thalach + thalach:relevel(sex,ref='male'), data = cleveland, family = 'binomial');summary(model_cp_sex)
rawresid_cp_sex <- residuals(model_cp_sex,"resp")
binnedplot(x=fitted(model_cp_sex),y=rawresid_cp_sex,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_cp_sex <- confusionMatrix(as.factor(ifelse(fitted(model_cp_sex) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_cp_sex
```

```{r, echo=F}
model_cp_sex <- glm(num ~ relevel(cp,ref='asymptomatic')*relevel(sex,ref='male') + trestbps + trestbps:relevel(sex,ref='male'), data = cleveland, family = 'binomial');summary(model_cp_sex)
rawresid_cp_sex <- residuals(model_cp_sex,"resp")
binnedplot(x=fitted(model_cp_sex),y=rawresid_cp_sex,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_cp_sex <- confusionMatrix(as.factor(ifelse(fitted(model_cp_sex) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_cp_sex

```

```{r, echo=F}

```

```{r, echo=F}

```

```{r, echo=F}
### Full model

model_full = glm(num ~ cp*exang + 
                   cp:sex +
                   cp:thal +
                   chol:cp +
                   oldpeak + 
                   oldpeak:cp + 
                   trestbps + 
                   trestbps:sex + 
                   sex +
                   thalach +
                   chol +
                   thal +
                   thal:age +
                   age,
                 data = cleveland, family = binomial)

model_full_2 = glm(num ~ cp + 
                   cp:sex +
                   cp:thal +
                   oldpeak + 
                   oldpeak:cp + 
                   sex +
                   thalach +
                   thal +
                   thal:age +
                   slope +
                   age,
                 data = cleveland, family = binomial)
anova(model_full, model_full_2)

summary(model_full)

rawresid_full <- residuals(model_full_2,"resp")
binnedplot(x=fitted(model_full_2),y=rawresid_full,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_full <- confusionMatrix(as.factor(ifelse(fitted(model_full_2) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_full
```

```{r, echo=F}
n <- nrow(cleveland)
step_model <- step(model_cp,scope=formula(model_full),direction="forward",
     trace=0,k = log(n))
summary(step_model)

rawresid_step <- residuals(step_model,"resp")
binnedplot(x=fitted(step_model),y=rawresid_step,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_step <- confusionMatrix(as.factor(ifelse(fitted(step_model) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_step
```

```{r, echo=F}
n <- nrow(cleveland)
step_model <- step(model_exang,scope=formula(model_full),direction="forward",
     trace=0,k = log(n))
summary(step_model)

rawresid_step <- residuals(step_model,"resp")
binnedplot(x=fitted(step_model),y=rawresid_step,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_step <- confusionMatrix(as.factor(ifelse(fitted(step_model) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_step
```
```{r, echo=F}

```

```{r, echo=F}
n <- nrow(cleveland)
step_model <- step(model_cpex,scope=formula(model_full),direction="forward",
     trace=0,k = log(n))
summary(step_model)

rawresid_step <- residuals(step_model,"resp")
binnedplot(x=fitted(step_model),y=rawresid_step,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_step <- confusionMatrix(as.factor(ifelse(fitted(step_model) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_step
```

```{r, echo=F}
model_cpsex <- glm(num ~ exang*sex, data = cleveland, family = 'binomial')
summary(model_cpsex)
rawresid_cpsex <- residuals(model_cpsex,"resp")
binnedplot(x=fitted(model_cpsex),y=rawresid_cpsex,xlab="Pred. probabilities",
           col.int="red4",ylab="Avg. residuals",main="Binned residual plot",col.pts="navy")
confmat_cpsex <- confusionMatrix(as.factor(ifelse(fitted(model_cpsex) >= 0.5, "Diagnosis","NoDiagnosis")),
                                as.factor(cleveland$num), positive = "Diagnosis")
confmat_cpsex

```